---
title: "Portal Data Report"
author: "Isabel Siles Asaff"
date: "9/30/2021"
output: html_document
---


## Purpose

Explore population dynamics of rodents at Portal site

This document show how to: 

1. Load data from project
2. Process into time series
3. Make visualizations

## Load in packages

```{r, message=FALSE} 
# remove the messages that pop up when you run the code
library(dplyr)
library(ggplot2)
```

## Read in data
```{r}
data <- read.csv("https://ndownloader.figshare.com/files/2292172")
head(data)
```

The data includes `r length(unique(data$species_id))` species idea
This helps you include code within the text using back tics
Errors in your code does not allow you to knit the Rmarkdown

## Create time series analysis

Counts for all species across time.
```{r}
time_series <- data %>%
  group_by(species_id, year) %>%
  summarize(count = n())
head(time_series)
```

## Plot time series
```{r, message=FALSE, echo=FALSE, cache=TRUE}
## echo runs the code but does not show the code
## cache makes the loading of this chunk faster 
ggplot(time_series, aes(x = year, y = count)) +
  geom_line() +
  facet_wrap(~species_id)
```

